### 2021-09-08 manuscript/synthetic_data.tex
finish methodology

%======================================================================================
\subsection*{Tests with data over an undulating observation surface.}
%======================================================================================

@@

We performed the upward continuations of the noise-corrupted total-field anomalies 
(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
the classical method (equation \ref{eq:estimated-p-parameter-space}), 
the convolutional equivalent layer (our method), and 
the classical approach in the Fourier domain.
The noise-free total-field anomalies produced by the synthetic sources at $z = -1, \, 300$ m 
(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = -1, \, 300$ m.

>>>>

%======================================================================================
\subsection*{Tests with data over an undulating observation surface}
%======================================================================================

@@

We performed the upward continuations of the noise-corrupted total-field anomalies 
(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
the classical method, the convolutional equivalent layer method (our method), and 
the classical approach in the Fourier domain.
The noise-free total-field anomalies produced by the synthetic sources at $z = -1, \, 300$ m 
(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
